---
title: "Plot heatmap from imported data (xlsx)"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load simulation data and pre-process
```{r} 
library(ggplot2)
library(data.table)
library(magrittr)

import.folder <- "./Model_results/"
save.id <- "best_model" 

#import.folder <- "./data/sim6/"
import.file.params <- paste0(import.folder,save.id,"_data_parameters.csv")
import.file.rho <- paste0(import.folder,save.id,"_data_rho_1.csv")
import.file.phi <- paste0(import.folder,save.id,"_data_phi_1.csv")
import.file.V <- paste0(import.folder,save.id,"_data_V_1.csv")

#data.rho <- read.table(import.file, sep="\t", header = TRUE)
data.params <- read.csv(import.file.params, header=FALSE)
data.params
data.rho.0 <- read.csv(import.file.rho, header=FALSE)
data.phi.0 <- read.csv(import.file.phi, header=FALSE)
data.V.0 <- read.csv(import.file.V, header=FALSE)

# Import "single-cell" data from simulations (for velocity)
data.xCells1 <- as.data.table( read.csv( paste0(import.folder,save.id,"_1cell/1cell_sim1_xCellAll.csv"), header=FALSE) ) %>% setNames(., "x.raw")
data.xCells2 <- as.data.table( read.csv( paste0(import.folder,save.id,"_1cell/1cell_sim2_xCellAll.csv"), header=FALSE) ) %>% setNames(., "x.raw")
data.xCells3 <- as.data.table( read.csv( paste0(import.folder,save.id,"_1cell/1cell_sim3_xCellAll.csv"), header=FALSE) ) %>% setNames(., "x.raw")

# Read off from data.params (!!)
T.max <- 8
L <- 1500
nT <- 100
nX <- 200
dX <- 2*L/nX
dT <- T.max/nT

# saving figures
save.folder <- "./Figures/"

```

```{r}
# Merge simulation data
data.rho.0 <- as.matrix(data.rho.0)
data.rho <- as.data.frame.table(data.rho.0)
data.rho[1:2] <- lapply(data.rho[1:2], as.numeric)
data.rho<-setNames(data.rho, c("X", "Time", "rho") )

data.phi.0 <- as.matrix(data.phi.0)
data.phi <- as.data.frame.table(data.phi.0)
data.phi[1:2] <- lapply(data.phi[1:2], as.numeric)
data.phi<-setNames(data.phi, c("X", "Time", "phi") )

data.V.0 <- as.matrix(data.V.0)
data.V <- as.data.frame.table(data.V.0)
data.V[1:2] <- lapply(data.V[1:2], as.numeric)
data.V<-setNames(data.V, c("X", "Time", "V") )

data.merged <- as.data.table( merge(merge(data.rho, data.phi), data.V ) )

# convert X to physical units
data.merged[ , X.micron := -L+(2*L)*(X-1)/(nX) ]
```

```{r}
# Merge simulated single cell track data
# initial position
data.xCells1$x0 = 0;
data.xCells2$x0 = -200;
data.xCells3$x0 = -400;
data.xCells1[, x0 := 0] %>% .[, location := 'Bone Front']
data.xCells2[, x0 := -200] %>% .[, location := 'In Bone']
data.xCells3[, x0 := -400] %>% .[, location := 'Further In Bone']

# correct positions w.r.t. x0 (only run once!)
data.xCells1$x = data.xCells1$x.raw - data.xCells1$x0
data.xCells2$x = data.xCells2$x.raw - data.xCells2$x0
data.xCells3$x = data.xCells3$x.raw - data.xCells3$x0

# time
data.xCells1$time = (1:nrow(data.xCells1) - 1)*dT
data.xCells2$time = (1:nrow(data.xCells2) - 1)*dT
data.xCells3$time = (1:nrow(data.xCells3) - 1)*dT

data.xCells.merged <- rbindlist( list(data.xCells1, data.xCells2, data.xCells3) )
data.xCells.merged
```

### Load experimental and pre-process
Load in vivo skull expansion data
```{r}
# Skull expansion data (in vivo)
data.skull.expansion <- fread('./Data/data_skull_expansion_series.csv')
data.skull.expansion[, lin.size.um := sqrt(area)*1000 ]
ggplot( data.skull.expansion, aes(x=time, y=lin.size.um) )+
  geom_point()

```

Load ex vivo imaging data (osteogenic front + cells)
```{r}
# Ex vivo image data
filename <- "./Data/data_ex_vivo_videos_1_to_4_all_interfaces.csv"
data.live.interface <- fread(filename, drop='V1')
#data.live.interface$data_set <- as.factor(data.live.interface$data_set)

# cell tracks
filename <- "./Data/data_ex_vivo_tracked_cells_all.csv"
data.live.cells <- fread(filename, drop='V1')
#data.live.cells$data_set <- as.factor(data.live.cells$data_set)

ggplot(data=data.live.interface[time <= 6], aes(x=time, y=interface_height, color=factor(data_set)))+
  geom_line()+
  ggtitle('interface')

ggplot(data=data.live.cells, aes(x=time, y=mean_displacement, color=factor(data_set), linetype=location ) )+
  geom_line()+
  ggtitle('ex vivo tracked cells')

```

```{r}
# Load and analyze tracked cell *velocities* (ex vivo)
velocities_file <- "./Data/Velocities_all_videos.csv"
velocities <- fread(velocities_file, drop='V1')

velocities[, X.origin := mean(.SD[Location=='Bone Front']$X0), by=.(Video) ]
velocities[, X0_new := X0 - X.origin, by=.(Video, Location)]
# velocities[Location=='Bone Front', mean(X0_new), by=.(Video)]

velocities.mean <- velocities[, .(X0.mean=mean(X0_new), V.mean=mean(Velocity), V.sd=sd(Velocity), n=.N), by=.(Video, Location) ]
velocities.mean2 <- velocities[, .(X0.mean.mean=mean(X0_new), V.mean.mean = mean(Velocity),
                                   X0.mean.sd=sd(X0_new), V.mean.sd=sd(Velocity)), by=.(Location) ]

# Plot experimental cell velocities
ggplot(velocities, aes(x=X0_new, y=Velocity, color=Location) )+
  facet_wrap(~Video)+
  geom_point()
```

Calculate relevant data frames
```{r}
## simulated front 
T.front.sim <- 0
T.all <- (seq(0:nT)-1)/nT*T.max
tmp <- as.data.table(data.phi) %>% .[phi < 0.5, .(X.min = min(X)), by=.(Time) ]
X.front.sim <- tmp$X.min*dX
X.front.sim <- X.front.sim - X.front.sim[1]
data.front.sim <- as.data.table( list(time=T.all, interface_height=X.front.sim) )

# simulated data shows step-like progression. Fit a linear function through simulation data.
# table(data.front.sim$interface_height)
model <- lm(interface_height ~ 0 + time, data=data.front.sim)
data.front.sim.2 <- data.table( time=c(0, T.max), interface_height=c(0,  0+model$coefficients[[1]]*T.max) )

## in vivo skull expansion front (estimate)
t1=13.5
t2=14.0
tmax <- 6
V.front.exp.invivo <- (mean(data.skull.expansion[time==t2]$lin.size.um) - mean(data.skull.expansion[time==t1]$lin.size.um) )/((t2-t1)*24)
data.front.in.vivo <- as.data.table( list(time=c(0, tmax), interface_height=c(0, tmax*V.front.exp.invivo)) )

## cell tracks
filename <- "./Data/data_ex_vivo_tracked_cells_all.csv"
data.live.cells <- fread(filename, drop='V1')
data.live.cells %>% setnames(., old=c("mean_displacement"), new=c("x"))

data.single.cells.merged <- rbindlist( list(ex.vivo=data.live.cells, simulated=data.xCells.merged), fill=TRUE, idcol="source")
data.single.cells.merged[, x_avg := mean(x), by=.(time, source, location)] %>%
  .[, x_sem := sd(x)/sqrt(.N), by=.(time, source, location)]

```

Merge all data into one df
```{r}
data.live.cells.filt <- data.live.cells[, c('time', 'x', 'data_set')]
#data.live.cells.filt <- data.live.cells[, c('time', 'mean_displacement', 'data_set')] %>% setnames(., c('time', 'x', 'data_set') )
data.xCells.merged.filt <- data.xCells.merged[location=='Bone Front', c('time', 'x')]

data.front.sim.2.filt <- data.front.sim.2[, c('time', 'interface_height')] %>% setnames(., c('time', 'x') )
data.front.in.vivo.filt <- data.front.in.vivo[, c('time', 'interface_height')] %>% setnames(., c('time', 'x') )

data.live.interface.filt <- data.live.interface[, c('time', 'interface_height', 'data_set')] %>% setnames(., c('time', 'x', 'data_set') )

data.merged.filt <- rbindlist( list(cells.ex.vivo=data.live.cells.filt, 
                cells.sim=data.xCells.merged.filt,
                front.sim=data.front.sim.2.filt,
                front.in.vivo=data.front.in.vivo.filt,
                front.ex.vivo=data.live.interface.filt), fill=TRUE, idcol="id" )

data.merged.filt[, location := ifelse(id %in% c("cells.ex.vivo", "cells.sim"), "cells", "front") ]
data.merged.filt[, source := ifelse(id=='front.in.vivo', 
                                    'in vivo', 
                                    ifelse(id %in% c("cells.ex.vivo", "front.ex.vivo"), "ex vivo", "sim") 
                                    )]
data.merged.filt[, x_avg := mean(x), by=.(time, id) ]
data.merged.filt[, x_sem := sd(x)/sqrt(.N), by=.(time, id) ]

data.merged.filt
```

-----------------------------------------------------------------------------------
## Plot simulated profile at specific times

```{r fig.width=8, fig.height=3}
## Plot profile of phi over multiple times
L.plot <- 1000
t.plot <- c(1, 51, 101)
tmp.plot <- data.merged[Time %in% t.plot & X.micron>-L.plot & X.micron<L.plot,]

ggplot(data=tmp.plot, aes(x=X.micron, y=phi, color=factor(Time)) )+
  geom_line()+
  labs(x=expression("Distance ("*mu*"m)"), y=expression(phi))+
  xlim(-L.plot, L.plot)+
  ylim(0, 1)+
  theme_bw()+
  theme(axis.text=element_text(size=16, colour="black"),
        axis.title=element_text(size=16,face="bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank() )
  #ggsave(filename=paste0(save.folder, paste0(save.id, "_plot_phi_T1_1_51_101.pdf")), width=8, height=3)
``` 

```{r}
tmp.plot$Time[tmp.plot$Time==1] = 0
tmp.plot$Time[tmp.plot$Time==51] = 3
tmp.plot$Time[tmp.plot$Time==101] = 6
tmp.plot
write.csv(tmp.plot, file = "/Users/ydang3/Documents/Projects_Dresden/Tabler_SkullWave/SkullWave/Code/For_publication/profiles.csv", row.names = FALSE)
```

### Plot simulated profile at specific time with experimentally tracked cells
```{r}

# Plot together with simulations
# With all data points
t.plot <- 1
tmp.plot <- data.merged[Time %in% t.plot & X.micron>-L.plot & X.micron<L.plot,]
ggplot(data=tmp.plot[X.micron>-1000 & X.micron<1000], aes(x=X.micron, y=V) )+
  geom_line()+
  geom_point(data=velocities, aes(x=X0_new, y=Velocity, shape=factor(Video)) )+
  labs(x=expression("Distance ("*mu*"m)"), y=expression(V))+
  theme(axis.text=element_text(size=16),
        axis.title=element_text(size=16,face="bold"))+
  theme_bw()

# Error bar plot
t.plot <- 1
tmp.plot <- data.merged[Time %in% t.plot & X.micron>-L.plot & X.micron<L.plot,]
ggplot(data=tmp.plot[X.micron>-1000 & X.micron<1000], aes(x=X.micron, y=V) )+
  geom_line()+
  geom_point(data=velocities.mean2, aes(x=X0.mean.mean, y=V.mean.mean) )+
  geom_errorbar(data=velocities.mean2, aes(x=X0.mean.mean, y=V.mean.mean, ymin = V.mean.mean-V.mean.sd, ymax = V.mean.mean+V.mean.sd)) + 
  geom_errorbarh(data=velocities.mean2, aes(x=X0.mean.mean, y=V.mean.mean, xmin = X0.mean.mean-X0.mean.sd, xmax = X0.mean.mean+X0.mean.sd))+
  labs(x=expression("Distance ("*mu*"m)"), y=expression(V))+
  theme_bw()+
  theme(aspect.ratio=3/4,
        axis.text=element_text(size=16),
        axis.title=element_text(size=16,face="bold") )
#ggsave( paste0(save.folder, save.id, '_cell_velocities_profile.pdf'), width=8, height=6  )
```
```{r}
# write.csv(velocities.mean2, file = "/Users/ydang3/Documents/Projects_Dresden/Tabler_SkullWave/SkullWave/Code/For_publication/temp.csv", row.names = FALSE)
# write.csv(tmp.plot[X.micron>-1000 & X.micron<1000], file = "/Users/ydang3/Documents/Projects_Dresden/Tabler_SkullWave/SkullWave/Code/For_publication/temp.csv", row.names = FALSE)
```

### Plot all interface data together
Merge everything together and plot
```{r}
# Plot result
ggplot(data=data.merged.filt, aes(x=time, y=x_avg, linetype=source, color=location)  )+
  geom_ribbon( aes(ymin=x_avg-x_sem, ymax=x_avg+x_sem, fill=location, color=NA, alpha=0.01) )+
  geom_line( lwd=1 )+
  labs(x="Time (hr)", y="Displacement (microns)")+
  theme_bw()+
  theme(aspect.ratio=3/4,
        axis.text=element_text(size=16),
        axis.title=element_text(size=16,face="bold") )+
  scale_color_brewer(palette = "Dark2", aesthetics = c("colour", "fill"))+
  xlim(0, tmax)+
  ylim(0, 120)
#ggsave( paste0(save.folder, save.id, '_plot_all_exp_vs_sim', '.pdf') )
```
```{r}
# data.merged.filt
# write.csv(data.merged.filt, file = "/Users/ydang3/Documents/Projects_Dresden/Tabler_SkullWave/SkullWave/Code/For_publication/temp.csv", row.names = FALSE)
```

### R session
```{r}
sessionInfo()
```